---
name: Constantinos 
surname: Eraclides
address: "26, The Living Quarter, St Mary's Gate, Nottingham, Nottinghamshire, NG1 1PF"
phone: +44 (0) 7907952098
email: "constantinos.eraclides@gmail.com"
github: constantinoseraclides
linkedin: constantinoseraclides
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman
header-includes:
  - \usepackage{colortbl}
  - \arrayrulecolor{white}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
```

# 
An enthusiastic individual recently finished from my postgraduate studies. In possession of robust quantitative, problem-solving, analytical and critical thinking skills, that aims to consolidate and expand upon, through real world challenges. 

# Education

```{r ed}
tribble(~when, ~what, ~with, ~where, ~why,
        "2020-2021", "M.Sc. Applied Statistics and Datamining (Merit)", "Fife, Scotland", "University of St Andrews", 
        list("Dissertation topic: Bayesian model/variable Selection, within the Bayesian framework.", "Worked on imbalanced classification with a real high-dimensional dataset where it was sparse on its true effects."),
        "2017-2020", "B.Sc. Mathematics (2:1)", "Nottingham, England", "University of Nottingham",  
        list("Final Year Modules: Scientific Computations and Numerical Analysis, Optimization, Stochastic Modelling, Statistical Inference, Applied Statistical Modelling, Multivariate Analysis"),
        "2009-2016", "Secondary School (Apolytirion, 88.89%)", "Nicosia, Cyprus", "The GC School of Careers", 
        list("A-levels: Mathematics (A*), Further Mathematics (A), Greek (B)")
        ) %>%
  detailed_entries(when = when, what = what, where = where, with = with, why = why)
```


# Professional Expirience

```{r exp}
tribble(
  ~when, ~what, ~with, ~where, ~why,
  "07/2019", "Internship", "Nicosia, Cyprus" , "Cronje & Yiannas Acctuaries and Consultants LTD",
  list("Learned how a professional actuarial environment operates.",
       "Worked in teams to complete various tasks approinted by our supervisor.",
       "Enhanced my attention to detail, teamwork and professional accountability skills"),
  "07/2016-09/2017", "Special Forces", "Nicosia, Cyprus", "Cyprus National Guard",
  list("Completing my mandatory army service that necessitated working with a group towards a common goal, which required camaraderie with my fellow soldiers.",
       "Went through exhaustive training, which pushed my tolerance boundaries beyond what I thought where my limits."),
  "12/2015-01/2016", "Shop Assistant and Deliveries", "Limasol, Cyprus", "SPECTUS Wines & Spirits Merchants",
  list("I was in charge for the preparation of large orders and their delivery during Christmas season where there is an increase in demand for wine and spirits.",
       "Earned customer service skills and punctuality."),
  "06/2013-09/2013", "Logistics Department", "Nicosia, Cyprus", "Hellenic Distribution Agency LTD", 
  list("Preparation of delivery notes to customers based on available sales data while optimizing delivery routes of van drivers.")
) %>%
  detailed_entries(when = when, what = what, where = where, with = with, why = why)
```

# Additional Skills
  * Languages: Greek(Native Language), English(Proficient)
  * Programming Skills: R/Python/MATLAB
  * Computer Skills: ECDL qualification (Skillfull in Excel & Word)
  * Teaching Skills: During my final year at the GC School of Careers I tutored on a weekly basis a fellow student with his A-level Mathematics
  
# References

```{r ref}
library(tidyverse)
library(knitr)
library(kableExtra)

table.tbl <- tibble("Dr Michail Papathomas" = c(
                         "Centre for Research into Ecological & Environmental Modelling",
                         "University of St Andrews",
                         "Email: m.papathomas@st-andrews.ac.uk",
                         "T: +44 (0)1334 461818"),
                    
                    "Dr Martin Edjvet" = c(
                             "Department of Mathematical Sciences ",
                             "University of Nottingham",
                             "Email: martin.edjvet@nottingham.ac.uk",
                             "T: +44 (0) 1159514932"))
table.tbl %>% 
  kable(format = "latex") %>%
  row_spec((table.tbl %>%
             nrow()), extra_latex_after = "\\arrayrulecolor{white}")

```


  
